### 2018-08-29 scripts/02-metrics/02-metric_conformity/README.Rmd
metric characterisation -> metrics

---
output: github_document
---

@@

```{r, results = "asis"}
extract_scripts_documentation(".", recursive = FALSE) %>% 
  arrange(ix) %>% 
    mutate(
    script = glue::glue("[`{id}`]({file})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>%
  select(order, script, description = title) %>%
  knitr::kable()
```

>>>>

---
output: 
  github_document:
    pandoc_args: --atx-headers
---

@@

```{r, results = "asis"}
render_scripts_documentation()
```
